---
title: "ggplot2 Learning"
author: "Lareina La Flair"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
    number_sections: true
    theme: lumen
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

packages <- c("dplyr", "wesanderson", "forcats", "plotly", "stringr", "tidyr", "data.table", "purrr")

# Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

# Packages loading
invisible(lapply(packages, library, character.only = TRUE))

#Load native datasets

data()
data("esoph")
head(esoph)
str(esoph)

data("mtcars")
head(mtcars)

mtcars$fcyl <- as.factor(mtcars$cyl)
mtcars$fam <- as.factor(mtcars$am)
str(mtcars)

 
data("iris")
head(iris)
str(iris)


data("USArrests")
head(USArrests)
str(USArrests)

data("midwest")
head(midwest)
str(USArrests)

oh <- midwest %>% 
  filter(state == "OH")

data("economics")
str(economics)

data("msleep")
str(msleep)

```

# Introduction

This is an introduction to data visualization with the R package `ggplot2` This summary stems from a DataCamp course **Introduction to Data Visualization with ggplot2**

There are three main elements: data, aesthetics, and geometries.

**Aesthetic mappings** (scales on which we map the data) are the cornerstone of the grammar of graphics plotting concept. This is where the magic happens - converting continuous and categorical data into visual scales that provide access to a large amount of information in a very short time.

Typically, the dependent variable is mapped onto the the y-axis and the independent variable is mapped onto the x-axis.

Color vs. fill: Typically, the color aesthetic changes the outline of a geom and the fill aesthetic changes the inside.

Attributes vs. aesthetics: arguments to set attributes of the plot, not map variables onto aesthetics.

Color: You can specify colors in R using hex codes: a hash followed by two hexadecimal numbers each for red, green, and blue ("#RRGGBB"). Hexadecimal is base-16 counting. You have 0 to 9, and A representing 10 up to F representing 15. Pairs of hexadecimal numbers give you a range from 0 to 255. "#000000" is "black" (no color), "#FFFFFF" means "white", and `"#00FFFF" is cyan (mixed green and blue).

A plot’s **geometry** dictates what visual elements will be used.

**Themes** layer will enable you to make publication quality plots directly in R




```{r }
```

# Scatterplots

Uses `geom_point()` to generate scatterplots!

Always consider overplotting, particularly in the following four situations:

- Large datasets
- Aligned values on a single axis
- Low-precision data
- Integer data
- Typically, alpha blending (i.e. adding transparency) is recommended when using solid shapes. Alternatively, you can use opaque, hollow shapes.

Small points are suitable for large datasets with regions of high density (lots of overlapping).


```{r scatt, eval = TRUE}

#Plot One: Scatterplot with means of each independent variable

#Create summary dataset

iris_summary <- iris %>% 
  group_by(Species) %>% 
  summarise_all(mean) 

#
ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width, col = Species)) +
  geom_point() +
# Different data with inherited aes to show means
  geom_point(data = iris_summary, shape = 15, size = 5)

#Alternative shape
ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width, col = Species)) +
  geom_point() +
# Different data with inherited aes to show means
  geom_point(data = iris_summary, shape = 21, size = 5, fill = "black", stroke = 2)

# Use geom_jitter for overfitting

ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width, col = Species)) +
  geom_jitter(alpha = 0.5) 
```

# Histograms

Useful for exploring the distribution of your independent variable. Set meaningful bin widths.

Histograms cut up a continuous variable into discrete bins and, by default, maps the internally calculated `count` variable (the number of observations in each bin) onto the y aesthetic. 

`geom_histogram` is a special case of `geom_bar` and the position argument that can take on the following values:

- stack (the default): Bars for different groups are stacked on top of each other.
- dodge: Bars for different groups are placed side by side.
- fill: Bars for different groups are shown as proportions.
- identity: Plot the values as they appear in the dataset.

A density plot is a representation of the distribution of a numeric variable. It uses a kernel density estimate to show the probability density function of the variable. Note that bandwidth selection will depend on the data. Guidance [here](https://r-coder.com/density-plot-r/#Kernel_density_bandwidth_selection)

```{r hist, eval=TRUE}

ggplot(iris, aes(x = Sepal.Width)) +
  geom_histogram(binwidth = 0.1, center = 0.05) 

#Overlapping histograms
ggplot(iris, aes(x = Sepal.Width, fill = Species)) +
  geom_histogram(binwidth = 0.1, center = 0.05, position = "dodge") +
   scale_fill_manual(values = wes_palette(3, name = "Zissou1", type = "continuous"))

#Fill
ggplot(iris, aes(x = Sepal.Width, fill = Species)) +
  geom_histogram(binwidth = 0.1, center = 0.05, position = "fill") +
   scale_fill_manual(values = wes_palette(3, name = "Zissou1", type = "continuous"))

#Density plots

iris %>%
    group_by(Species) %>%
    ggplot(mapping = aes(x = Petal.Width)) + 
        geom_density(bw = 0.09,  fill = "gold") +
        labs(x = "Petal Width") + 
        facet_wrap(~Species, labeller = "label_both")

```

# Bar charts

We have three position options:

- stack: The default
- dodge: Preferred
- fill: To show proportions


```{r bar, eval=TRUE}

# Fill

ggplot(mtcars, aes(fcyl, fill = fam)) +
  geom_bar() +
  scale_fill_manual(values = wes_palette(2, name = "Zissou1", type = "continuous"))

#Fill - conditional bar chart

ggplot(mtcars, aes(fcyl, fill = fam)) +
  # Set the position to "fill"
  geom_bar(position = "fill") +  
  ylab("proportion") +
  scale_fill_manual(values = wes_palette(2, name = "Zissou1", type = "continuous"))


#Dodge
ggplot(mtcars, aes(fcyl, fill = fam)) +
  # Change the position to "dodge"
  geom_bar(position = "dodge") +
  scale_fill_manual(values = wes_palette(2, name = "Zissou1", type = "continuous"))

#Overlapping bar plots
ggplot(mtcars, aes(cyl, fill = fam)) +
  # Change position to use the functional form, with width 0.2
  geom_bar(position = position_dodge(width = 0.2), alpha = 0.6) +
   scale_fill_manual(values = wes_palette(2, name = "Zissou1", type = "continuous"))

#Scale

ggplot(esoph, aes(alcgp, fill = agegp)) +
  # Add a bar layer with position "fill"
  geom_bar(position = "fill") +
  scale_fill_manual(values = wes_palette(6, name = "Zissou1", type = "continuous"))



```

# Line charts

Excellent for timeseries data!

Use color to distinguish between series. Also can use `geom_area` which defaults to stack. Use position = "fill" to show proportional trends over time. Use `geom_ribbon` to examine overlapping areas.

Use the `economics` dataset to look at how the median unemployment time and the unemployment rate (the number of unemployed people as a proportion of the population) change over time.

```{r line, eval=TRUE, echo=FALSE}

ggplot(economics, aes(date, unemploy)) +
  geom_line()

economics <- economics %>% 
  mutate(quartile = ntile(pop, 4))

economics$fquart <- as.factor(economics$quartile)

# Plot multiple time-series by grouping by species
ggplot(economics, aes(x = date, y = unemploy)) +
  geom_line(aes(group = fquart))

    
ggplot(economics, aes(x = date, y = unemploy, color = fquart)) +
  geom_line()

ggplot(storms, aes(x = year, y = wind, color = category)) +
  geom_line()




```

# Themes

Defining your own theme!

Built-in themes

- theme_gray() is the default
- theme_bw() is useful when you use transparency
- theme_classic() is more traditional
- theme_void() removes everything but the data


```{r themes, eval = TRUE}

theme_iris <- theme(text = element_text(family = "serif", size = 14),
              rect = element_blank(),
              panel.grid = element_blank(), 
              title = element_text(color = "#8b0000"),
              axis.line = element_line(color = "black"))

m <- ggplot(iris, aes(x = Sepal.Width)) +
          geom_histogram(binwidth = 0.1, center = 0.05)

m + theme_iris

m + theme_iris +
  theme(axis.line.x  = element_blank())

#apply custom theme
ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width, col = Species)) +
  geom_jitter(alpha = 0.5) +
  theme_iris

#stock themes in ggthemes

library(ggthemes)

m + theme_tufte()
m + theme_fivethirtyeight()

#code below for dumbbell plots
# Set the color scale
#palette <- brewer.pal(5, "RdYlBu")[-(2:4)]


# ggplot(gm2007, aes(x = lifeExp, y = country, color = lifeExp)) +
#   geom_point(size = 4) +
#   geom_segment(aes(xend = 30, yend = country), size = 2) +
#   geom_text(aes(label = round(lifeExp,1)), color = "white", size = 1.5) +
#   scale_x_continuous("", expand = c(0,0), limits = c(30,90), position = "top") +
#   scale_color_gradientn(colors = palette)

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
