---
title: "ggplot2 Learning"
author: "Lareina La Flair"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
    number_sections: true
    theme: lumen
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

packages <- c("dplyr", "wesanderson", "forcats", "plotly", "stringr", "tidyr", "data.table", "purrr")

# Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

# Packages loading
invisible(lapply(packages, library, character.only = TRUE))

#Load native datasets

data()
data("esoph")
head(esoph)
str(esoph)

data("mtcars")
head(mtcars)

mtcars$fcyl <- as.factor(mtcars$cyl)
mtcars$fam <- as.factor(mtcars$am)
str(mtcars)

 
data("iris")
head(iris)
str(iris)


data("USArrests")
head(USArrests)
str(USArrests)

data("midwest")
head(midwest)
str(USArrests)

oh <- midwest %>% 
  filter(state == "OH")

data("economics")
str(economics)

data("msleep")
str(msleep)

```

# Introduction

This is an introduction to data visualization with the R package `ggplot2` This summary stems from a DataCamp course **Introduction to Data Visualization with ggplot2**

There are three main elements: data, aesthetics, and geometries.

**Aesthetic mappings** (scales on which we map the data) are the cornerstone of the grammar of graphics plotting concept. This is where the magic happens - converting continuous and categorical data into visual scales that provide access to a large amount of information in a very short time.

Typically, the dependent variable is mapped onto the the y-axis and the independent variable is mapped onto the x-axis.

Color vs. fill: Typically, the color aesthetic changes the outline of a geom and the fill aesthetic changes the inside.

Attributes vs. aesthetics: arguments to set attributes of the plot, not map variables onto aesthetics.

Color: You can specify colors in R using hex codes: a hash followed by two hexadecimal numbers each for red, green, and blue ("#RRGGBB"). Hexadecimal is base-16 counting. You have 0 to 9, and A representing 10 up to F representing 15. Pairs of hexadecimal numbers give you a range from 0 to 255. "#000000" is "black" (no color), "#FFFFFF" means "white", and `"#00FFFF" is cyan (mixed green and blue).

A plot’s **geometry** dictates what visual elements will be used.

**Themes** layer will enable you to make publication quality plots directly in R




```{r }
```

# Scatterplots


```{r }
```

# Histograms



```{r hist, eval=TRUE}


```

# Bar charts

We have three position options:

- stack: The default
- dodge: Preferred
- fill: To show proportions


```{r bar, eval=TRUE, echo=FALSE}

#Fill

ggplot(mtcars, aes(fcyl, fill = fam)) +
  # Set the position to "fill"
  geom_bar(position = "fill") +  
  scale_fill_manual(values = wes_palette(2, name = "Zissou1", type = "continuous"))


#Dodge
ggplot(mtcars, aes(fcyl, fill = fam)) +
  # Change the position to "dodge"
  geom_bar(position = "dodge") +
  scale_fill_manual(values = wes_palette(2, name = "Zissou1", type = "continuous"))

#Overlapping bar plots
ggplot(mtcars, aes(cyl, fill = fam)) +
  # Change position to use the functional form, with width 0.2
  geom_bar(position = position_dodge(width = 0.2), alpha = 0.6) +
   scale_fill_manual(values = wes_palette(2, name = "Zissou1", type = "continuous"))

#Scale

ggplot(esoph, aes(alcgp, fill = agegp)) +
  # Add a bar layer with position "fill"
  geom_bar(position = "fill") +
  scale_fill_manual(values = wes_palette(6, name = "Zissou1", type = "continuous"))



```

# Line charts

Excellent for timeseries data!

Use color to distinguish between series. Also can use `geom_area` which defaults to stack. Use position = "fill" to show proportional trends over time. Use `geom_ribbon` to examine overlapping areas.

Use the `economics` dataset to look at how the median unemployment time and the unemployment rate (the number of unemployed people as a proportion of the population) change over time.

```{r line, eval=TRUE, echo=FALSE}

ggplot(economics, aes(date, unemploy)) +
  geom_line()

economics <- economics %>% 
  mutate(quartile = ntile(pop, 4))

economics$fquart <- as.factor(economics$quartile)

# Plot multiple time-series by grouping by species
ggplot(economics, aes(x = date, y = unemploy)) +
  geom_line(aes(group = fquart))

    
ggplot(economics, aes(x = date, y = unemploy, color = fquart)) +
  geom_line()

ggplot(storms, aes(x = year, y = wind, color = category)) +
  geom_line()



```


```{r kjv}


```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
